Modal type theory based on the intuitionistic epistemic logic

### 2018-01-20 article.tex
some text

  Let us define natural transformations:
  \begin{itemize}
  \item $\eta : Id_{\mathcal{C}(\lambda)} \to \mathcal{K}$, such that forall $A \in Ob_{\mathcal{C}(\lambda)}$, $\eta_A = [x, {\bf pure \:} x] \in Hom_{\mathcal{C}(\lambda)}(A, {\bf K}A)$;

  \item $\ast_{A,B} : {\bf K}A \times {\bf K}B \to {\bf K}(A \times B)$
  \end{itemize}
\end{defin}

@@

$\begin{array}{lll}
&\eta_B \circ f = & \\
&[y, {\bf pure \:} y] \circ [x, M] = & \\
&[x, {\bf pure \:} y [y := M]] =& \\
&[x, {\bf pure \:} M]& \\
&\text{On the other hand}& \\
&\text{fmap } f \circ \eta_A = &\\
&[z, {\bf let \: pure \:} x = z {\: \bf in \:} M] \circ [x, {\bf pure \: x}] = & \\
&[x, {\bf let \: pure \:} x = z {\: \bf in \:} M [z := {\bf pure \:} x]] = & \\
&[x, {\bf let \: pure \:} x = {\bf pure \: x} {\: \bf in \:} M] = & \\
&[x, {\bf pure \:} M [x := x]] = & \\
&[x, {\bf pure \:} M]&
\end{array}$

>>>>

  Let us define natural transformations:

  1) $\eta:Id \Rightarrow \mathcal{K}$, s. t. $\forall A \in Ob_{\mathcal{C}(\lambda)}$, $\eta_A = [x, {\bf pure \:} x] \in Hom_{\mathcal{C}(\lambda)}(A, {\bf K}A)$;

  2) $\ast_{A,B}:{\bf K}A \times {\bf K}B \to {\bf K}(A \times B)$.
\end{defin}

@@

$\begin{array}{lll}
&\eta_B \circ f = & \text{By the definition} \\
&[y, {\bf pure \:} y] \circ [x, M] = & \text{By the definition of composition}\\
&[x, {\bf pure \:} y [y := M]] = & \text{By substitution}\\
&[x, {\bf pure \:} M]& \\
& &\\
&\text{On the other hand:}& \\
&\text{fmap } f \circ \eta_A = & \text{By the definiton} \\
&[z, {\bf let \: pure \:} x = z {\: \bf in \:} M] \circ [x, {\bf pure \: x}] = & \text{By the definition of composition}\\
&[x, {\bf let \: pure \:} x = z {\: \bf in \:} M [z := {\bf pure \:} x]] = & \text{By substitution} \\
&[x, {\bf let \: pure \:} x = {\bf pure \: x} {\: \bf in \:} M] = & \text{$\beta$-reduction rule}\\
&[x, {\bf pure \:} M [x := x]] = & \text{By substitution}\\
&[x, {\bf pure \:} M]&
\end{array}$
